\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-05-01 ase20/eval.tex
Updated numbers in 5.2 / Table 5

To evaluate the correctness of \( \tool \), we checked whether the
extracted semantics from the latest ECMAScript (ES10) passes Test262
as of February 28, 2019, when ES10 was branched out.
To focus on the core language semantics of JavaScript, we completed
only necessary parts missing from the extracted AST-IR translator.
As Figure~\ref{fig:all-version}(a) shows, for the abstract algorithms
in ES10, \inred{8,901} steps out of \inred{9,674} steps are
automatically compiled by \textsf{Algorithm Compiler}.
Among the remaining \inred{773} steps, we manually implemented all
missing steps for the core language semantics (\inred{221} steps) and
the essential parts of the built-in libraries (\inred{XX} steps out of
\inred{552}).  We also manually implemented \textsf{Global Setting}
as described in Section~\ref{sec:compiler-impl} for the core language features.
Note that we do not support minor language features such as the
non-strict mode, modules, early errors before actual execution, and
inessential built-in objects.
Among \inred{XX,XXX} tests in Test262, we filtered out \inred{XX,XXX}
tests as summarized in Table~\ref{table:test262}.  To focus on ES10,
we excluded \inred{X,XXX} tests for annexes, internationalization, and
in-progress features.  We also filted out \inred{X,XXX} tests that use
minor language features.
Finally, for \inred{XX,XXX} applicable tests, the extracted semantics
failed for \inred{XXX} tests.

@@

After resolving the nine specification errors in ES10, we extracted a
semantics from the revised specification.  The extracted semantics
from the revised ES10 passed all \inred{XX,XXX} applicable tests in Test262,
which shows that \( \tool \) extracts an IR-based formal semantics
from ECMAScript correctly.  In addition, the evaluation witnesses that
\( \tool \) can detect specification errors effectively.
We could detect not only five previously-known errors
but also four new errors.  We believe that \( \tool \) bridges gaps
between ECMAScript written in a natural language and executable tests
in Test262.

@@

\footnotesize
    \scode{matchAll} of \scode{String} &
    0 &
    0 &
    9/9 &
    5/5 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \scode{import()} &
    0 &
    2 &
    22/23 &
    0/0 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \scode{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \scode{Promise.allSettled } &
    0 &
    0 &
    79/85 &
    50/50 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \scode{globalThis} &
    0 &
    0 &
    1/1 &
    1/1 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

\footnotesize
    \scode{for-in}  mechanics &
    0 &
    0 &
    36/37 &
    0/0 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

\footnotesize    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

\footnotesize   Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

    \scode{import.meta} &
    0 &
    2 &
    15/15 &
    0/0 &
    \inred{XXXXX}/\inred{XXXXX}\\\hline

>>>>

To evaluate the correctness of \( \tool \), we checked whether the
extracted semantics from the latest ECMAScript (ES10) passes Test262
as of February 28, 2019, when ES10 was branched out.
To focus on the core language semantics of JavaScript, we completed
only necessary parts missing from the extracted AST-IR translator.
As Figure~\ref{fig:all-version}(a) shows, for the abstract algorithms
in ES10, 9,627 steps out of 10,101 steps are
automatically compiled by \textsf{Algorithm Compiler}.
Among the remaining 474 steps, we manually implemented all
missing steps for the core language semantics (137 steps) and
the essential parts of the built-in libraries (\inred{XX} steps out of
337).  We also manually implemented \textsf{Global Setting}
as described in Section~\ref{sec:compiler-impl} for the core language features.
Note that we do not support minor language features such as the
non-strict mode, modules, early errors before actual execution, and
inessential built-in objects.
Among 35,990 tests in Test262, we filtered out 17,926
tests as summarized in Table~\ref{table:test262}.  To focus on ES10,
we excluded 7,038 tests for annexes, internationalization, and
in-progress features.  We also filted out 10,888 tests that use
minor language features.
Finally, for 18,064 applicable tests, the extracted semantics
failed for \inred{XXX} tests.

@@

After resolving the nine specification errors in ES10, we extracted a
semantics from the revised specification.  The extracted semantics
from the revised ES10 passed all 18,064 applicable tests in Test262,
which shows that \( \tool \) extracts an IR-based formal semantics
from ECMAScript correctly.  In addition, the evaluation witnesses that
\( \tool \) can detect specification errors effectively.
We could detect not only five previously-known errors
but also four new errors.  We believe that \( \tool \) bridges gaps
between ECMAScript written in a natural language and executable tests
in Test262.

@@

\footnotesize
    \scode{matchAll} of \scode{String} &
    0 &
    0 &
    9/9 &
    5/5 &
    \inred{XXXXX}/18,064\\\hline

    \scode{import()} &
    0 &
    2 &
    22/23 &
    0/0 &
    \inred{XXXXX}/18,064\\\hline

    \scode{BigInt} &
    4 &
    0 &
    258/323 &
    \inred{207}/207 &
    \inred{XXXXX}/18,064\\\hline

    \scode{Promise.allSettled } &
    0 &
    0 &
    79/85 &
    50/50 &
    \inred{XXXXX}/18,064\\\hline

    \scode{globalThis} &
    0 &
    0 &
    1/1 &
    1/1 &
    \inred{XXXXX}/18,064\\\hline

\footnotesize
    \scode{for-in}  mechanics &
    0 &
    0 &
    36/37 &
    0/0 &
    \inred{XXXXX}/18,064\\\hline

\footnotesize    Optional Chaining &
    3 &
    3 &
    72/74 &
    19/19 &
    \inred{XXXXX}/18,064\\\hline

\footnotesize   Nullish Coalescing Op. &
    1 &
    4 &
    10/10 &
    21/21 &
    \inred{XXXXX}/18,064\\\hline

    \scode{import.meta} &
    0 &
    2 &
    15/15 &
    0/0 &
    \inred{XXXXX}/18,064\\\hline
